P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2025-04-28 sage_latex_template/manuscript.tex
Add table for compilers
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

% Changes during review
\newcommand{\RMchange}[1]{{\setlength{\fboxsep}{0pt}\colorbox{purple!70}{#1}}}
%\newcommand{\RMchange}[1]{#1}

@@

The icc (ICC) 2021.10.0 20230609 compiler was used for CPU experiments (except in the JUWELS cluster), with the \emph{-Ofast -xCORE-AVX512 -qopt-zmm-usage=high} flags for Fritz / Ice Lake (AVX512) and \emph{-Ofast -march=core-avx2} flags for Milan (AVX2).
For CUDA, we use the NVCC compiler V12.1.r12.1 for the single GPU experiments, and the same flags used for Milan (AVX2) since it is the host processor in the systems with the A40/A100 GPUs.
In the JUWELS Booster, we used the Intel(R) oneAPI DPC++/C++ Compiler 2023.2.0 (2023.2.0.20230721) together with NVCC V12.2.91, and the same flags as used for Milan since both CPUs have AVX2 with FMA as the largest SIMD vector extension available.
We make use of the Likwid toolkit V5.3 (\cite{likwid}) to pin tasks to specific CPU cores and measure HPM counters in the target CPU (Ice Lake) for the single core experiments, where P4IRS is able to properly generate the instrumentation markers and MD-Bench kernels are already instrumented.

>>>>

% Changes during review
\usepackage{soul}
\usepackage{xcolor}

\DeclareRobustCommand{\RMchange}[1]{{\sethlcolor{cyan}\hl{#1}}}
%\newcommand{\RMchange}[1]{{\colorbox{purple!70}{#1}}}
%\newcommand{\RMchange}[1]{{\setlength{\fboxsep}{0pt}\colorbox{purple!70}{#1}}}
%\newcommand{\RMchange}[1]{#1}

@@

\begin{table*}[htb]
    \centering
    \begin{tabular}{c|c|c}
%        \hline
        Target & Compiler & Flags \\
        \hline
        Ice Lake & ICC 2021.10.0 & \emph{-Ofast -xCORE-AVX512 -qopt-zmm-usage=high} \\
        Milan & ICC 2021.10.0 & \emph{-Ofast -march=core-avx2} \\
        A40 & NVCC 12.1.r12.1 & \emph{-Ofast -march=core-avx2} \\
        A100 (single GPU) & NVCC 12.1.r12.1 & \emph{-Ofast -march=core-avx2} \\
        A100 (JUWELS Booster) & NVCC 12.2.91 & \emph{-Ofast -march=core-avx2} \\
        Rome (JUWELS Booster) & ICX 2023.2.0 & \emph{-Ofast -march=core-avx2} \\
%        \hline
    \end{tabular}
    \caption{\RMchange{Compiler and flag specifications used for the experiments in this paper.}}
    \label{tab:compilers}
\end{table*}

\autoref{tab:compilers} \RMchange{displays the compiler and flags used for the experiments in this paper.}
The icc (ICC) 2021.10.0 20230609 compiler was used for CPU experiments (except in the JUWELS cluster), with the \emph{-Ofast -xCORE-AVX512 -qopt-zmm-usage=high} flags for Fritz / Ice Lake (AVX512) and \emph{-Ofast -march=core-avx2} flags for Milan (AVX2).
For CUDA, we use the NVCC compiler V12.1.r12.1 for the single GPU experiments, and the same flags used for Milan (AVX2) since it is the host processor in the systems with the A40/A100 GPUs.
In the JUWELS Booster, we used the Intel(R) oneAPI DPC++/C++ \RMchange{"ICX"} Compiler 2023.2.0 (2023.2.0.20230721) \RMchange{as a backend compiler for} NVCC V12.2.91, and the same flags used for Milan since both CPUs have AVX2 with FMA as the largest SIMD vector extension available.
We make use of the Likwid toolkit V5.3 (\cite{likwid}) to pin tasks to specific CPU cores and measure HPM counters in the target CPU (Ice Lake) for the single core experiments, where P4IRS is able to properly generate the instrumentation markers and MD-Bench kernels are already instrumented.
